Text as Policy: \\ Measuring Policy Similarity through Bill Text Reuse

### 2017-02-11 manuscript/main.tex

We take a multi-pronged approach to evaluating the performance of text reuse in measuring the consideration and adoption of similar laws. First, we investigate the relationship between the ideological distance of the legislators that proposed two bills and the text reuse scores between these bills. Second, we assess the how well policy diffusion networks that have been established by previous research can be predicted using the amount of text reuse between states. And third, we use data on equivalent bills collected by the National Conference of State Legislatures to build an evaluation data set containing true policy overlap to assess the accuracy of text reuse in predicting policy overlap. We find that a high degree of text reuse between bills provides a precise signal of the presence of similar policies within the bills.

>>>>

We take a multi-pronged approach to evaluating the performance of text reuse in measuring the consideration and adoption of similar laws. First, we investigate the relationship between the ideological distance of the legislators that proposed two bills and the text reuse scores between these bills. Second, we assess the how well policy diffusion networks that have been established by previous research can be predicted using the amount of text reuse between states. And third, we use data on equivalent bills collected by the National Conference of State Legislatures to build an evaluation data set containing true policy overlap to assess the accuracy of text reuse in predicting policy overlap. We find that a high degree of text reuse between bills provides a precise signal of the presence of similar policies within the bills. The findings and open questions offered by our work contribute beyond the study of public policy diffusion or legislative politics. We add to the growing methodological literature in political science and public policy that is focused on the use of text-as-data methods for measurement tasks \citep[see, e.g.,][]{laver2003extracting,martin2008robust,lowe2013validating,grimmer2013text,monroe2008fightin,blair2016national}. Furthermore, the methodological approach we present would be applicable to any of the several lines of research in political science and public policy that draw upon text corpora to operationalize variables of interest \citep[see, e.g.,][]{hart1990evolution,van2008parsing,young2012affective,mikhaylov2012coder,mondou2014policy,witting2015measuring}.
